
\cleardoublepage

\phantomsection
\addcontentsline{toc}{chapter}{Acknowledgements}

\begin{acknowledgements}

First and foremost, I would like to express my sincere gratitude to my advisor Professor Wayne Luk.
Only through his enthusiasm for research, timely words of encouragement, and immense amount of patient, have I been able to develop into the person that I am today.
His guidance has helped me improve my papers, presentations, and this thesis tremendously.
His trust has always supported me in all the time of research.
I could not have imagined having a better advisor for my Ph.D. study.

I would like to thank my secondary advisor Professor Peter Y.K. Cheung and my master program's advisor Professor Philip Leong.
They open the door for me to the research of reconfigurable computing and inspire me throughout the years.
I deeply appreciate their insightful comments.

%I am indebted to Professor Neil Audsley and Professor Jeremy Bradley for serving as my thesis examiner. 
Special thanks are due to Dr. Alison Eele and Professor Jan Maciejowski in University of Cambridge, and Dr. Benjamin Cope and Dr. Kathryn Cobden in Altera Corporation, for their collaboration in our project on sequential Monte Carlo methods and air traffic management.

It is also a real privilege for me to study in the Custom Computing Group, Department of Computing at Imperial College London.
Thanks are specially given to Maciej Kurek, Xinyu Niu, Dr.~Kuen Hung Choi, Gary Chow and Dr.~Ka-Wai Kwok for all the invaluable discussion and collaboration.
Thank you also to my past and present colleagues in the lab: James Arram, Dr.~Tobias Becker, Dr.~Brahim Betkaoui, Dr.~Pavel Burovskiy, Dr.~Bridgette Cooper, Kit Cheung, Dr.~Gabriel De Figueiredo Coutinho, Stewart Denholm, Paul Grigoras, Ce Guo, Liucheng Guo, Dr.~Eddie Hung, Gordon Inggs, Dr.~Qiwei Jin, Dr.~Andrien Le Masle, Nicholas Ng, Shengjia Shao, Dr.~Timothy Todman, Dr.~Anson Tse, Jinzhe Yang.
I extend my gratitude to the project students, James Targett, Marlon Wijeyasinghe, Jake Humphrey, Georgios Skouroupathis, in the Department of Computing and the Department of Electrical and Electronic Engineering for all the productive work.

I am grateful for an internship opportunity working in ARM Ltd. at Cambridge, UK.
It was a fruitful experience and I would like to thank my manager and mentor William Wang for sharing his expertise and broadening my knowledge.

I am thankful for the generous financial support provided by the Croucher Foundation, UK Engineering and Physical Sciences Research Council, and the European Union Seventh Framework Programme.

Lastly, my warmest thanks go to my wife, Kaijia, for her continued support throughout the years.
She is such an excellent cook that keeps me eat and study well.

\end{acknowledgements}
