
\cleardoublepage

\phantomsection
\addcontentsline{toc}{chapter}{Publications}

\begin{publications}

%\begingroup
%\renewcommand{\chapter}[2]{}%
%\input{myrefs.bbl}
%\endgroup

The following publication contributes to the precision optimisation of data-path in Chapter~\ref{ch:precision}:
\begin{itemize}
\item T. C. P. Chau, K.-W. Kwok, G. C. T. Chow, K. H. Tsoi, Z. Tse, P. Y. K. Cheung, and W. Luk, ``Acceleration of real-time proximity query for dynamic active constraints,'' in \textit{Proceedings of International Conference on Field-Programmable Technology}, 2013.%pp. 206-213.
\end{itemize}

The following publications contribute to the run-time adaptation of system configuration in Chapter~\ref{ch:adaptation}:
\begin{itemize}
\item T. C. P. Chau, X. Niu, A. Eele, J. M. Maciejowski, P. Y. K. Cheung, and W. Luk, ``Mapping adaptive particle filters to heterogeneous reconﬁgurable systems,'' \textit{ACM Transactions on Reconﬁgurable Technology and Systems}, vol. 7, no. 4, 2014.
\item T. C. P. Chau, X. Niu, A. Eele, W. Luk, P. Y. K. Cheung, and J. M. Maciejowski, ``Heterogeneous reconfigurable system for adaptive particle filters in real-time applications,'' in \textit{Proceedings of International Symposium Applied Reconfigurable Computing}, 2013.%pp. 1-12.
\end{itemize}

The following publication contributes to the design flow for domain-specific reconfigurable applications in Chapter~\ref{ch:tool}:
\begin{itemize}
\item T. C. P. Chau, M. Kurek, J. S. Targett, J. Humphrey, G. Skouroupathis, A. Eele, J. Maciejowski, B. Cope, K. Cobden, P. Leong, P. Y. K. Cheung, and W. Luk, ``SMCGen: Generating reconfigurable design for sequential Monte Carlo applications,'' in \textit{Proceedings of International Symposium on Field-Programmable Custom Computing Machines}, 2014.%pp. 141-148.
\end{itemize}

The following publication contributes to the parameter optimisation approach in Chapter~\ref{ch:tool}:
\begin{itemize}
\item M. Kurek, T. Becker, T. C. P. Chau, and W. Luk, ``Automating optimization of reconfigurable designs,'' in \textit{Proceedings of International Symposium on Field-Programmable Custom Computing Machines}, 2014.%pp. 201-213.
\end{itemize}

\pagebreak
The following publications contribute to the air traffic management application evaluated in Chapter~\ref{ch:tool}:
\begin{itemize}
\item T. C. P. Chau, J. S. Targett, M.Wijeyasinghe, W. Luk, P. Y. K. Cheung, B. Cope, A. Eele, and J. M. Maciejowski, ``Accelerating sequential Monte Carlo method for real-time air traffic management,'' \textit{SIGARCH Computer Architecture News}, vol. 41, no. 5, 2013.
\item A. Eele, J. M. Maciejowski, T. C. P. Chau, and W. Luk, ``Parallelisation of sequential Monte Carlo for real-time control in air traffic management,'' in \textit{Proceedings of International Conference Decision and Control}, 2013.
\item A. Eele, J. M. Maciejowski, T. C. P. Chau, and W. Luk, ``Control of aircraft in the terminal manoeuvring area using parallelised sequential Monte Carlo,'' in \textit{Proceedings of AIAA Conference on Guidance, Navigation, and Control}, 2013.
\end{itemize}

The following publications are published during my research but they are not discussed in this thesis:
\begin{itemize}
\item X. Niu, T. C. P. Chau, Q. Jin, W. Luk, and Q. Liu, ``Automating elimination of idle functions by run-time reconfiguration,'' in \textit{Proceedings of International Symposium on Field-Programmable Custom Computing Machines}, 2013.%pp. 97-104.
\item T. C. P. Chau, W. Luk, and P. Y. K. Cheung, ``Roberts: Reconfigurable platform for benchmarking real-time systems,'' \textit{SIGARCH Computer Architecture News}, vol. 40, no. 5, 2012.
\item T. C. P. Chau, W. Luk, P. Y. K. Cheung, A. Eele, and J. M. Maciejowski, ``Adaptive sequential Monte Carlo approach for real-time applications,'' in \textit{Proceedings of International Conference Field Programmable Logic and Applications}, 2012.%pp. 527-530.
\end{itemize}

\end{publications}
